Mental Health Screening in CF

### 2023-01-10 Emily Muther/mental_health_screening.qmd
Update mental_health_screening.qmd

```{python}
import pandas as pd
# Data import
gad7 = pd.read_csv("/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Emily Muther/Mental Health Screening/Data_Raw/GAD-7_General_Anxiety_Disorder_Full_Data_data_11-15-22.csv")
gad7 = gad7[['PAT_MRN_ID','CONTACT_DATE','AGE AT CONTACT ','GAD-7 Total Score','GAD-7 Totals']]
gad7.dropna(axis=0,inplace=True)
gad7.drop_duplicates(inplace=True)
phq9 = pd.read_csv("/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Emily Muther/Mental Health Screening/Data_Raw/PHQ-9_Full_Data_data_11-11-22.csv")
phq9 = phq9[['PAT_MRN_ID','CONTACT_DATE','AGE AT CONTACT ','PHQ-9 Total Score (calculated)','PHQ-9 Totals']]
phq9.dropna(axis=0,inplace=True)
phq9.drop_duplicates(inplace=True)
psc = pd.read_csv("/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Emily Muther/Mental Health Screening/Data_Raw/PSC_Full_Data_data_11-11-22.csv")
psc = psc[['PAT_MRN_ID','CONTACT_DATE','AGE AT CONTACT ','Score','PSC Totals']]
psc.dropna(axis=0,inplace=True)
psc.drop_duplicates(inplace=True)
# Merge
df = gad7.merge(phq9,on=['PAT_MRN_ID','CONTACT_DATE','AGE AT CONTACT '],how="outer")
df = df.merge(psc,on=['PAT_MRN_ID','CONTACT_DATE','AGE AT CONTACT '],how="outer")
# Rename
df.rename({'PAT_MRN_ID':'ID','CONTACT_DATE':'Date','AGE AT CONTACT ':'Age','GAD-7 Total Score':'GAD-7 Total','GAD-7 Totals':'GAD-7 Group','PHQ-9 Total Score (calculated)':'PHQ-9 Total','PHQ-9 Totals':'PHQ-9 Group','Score':'PSC-17 Total','PSC Totals':'PSC-17 Group'},inplace=True,axis=1)
```

>>>>

```{python}
import pandas as pd
# Data import
gad7 = pd.read_csv("/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Emily Muther/Mental Health Screening/Data_Raw/GAD-7_General_Anxiety_Disorder_Full_Data_data_11-15-22.csv")
gad7 = gad7[['PAT_MRN_ID','CONTACT_DATE','AGE AT CONTACT ','GAD-7 Total Score','GAD-7 Totals']]
gad7.dropna(axis=0,inplace=True)
gad7.drop_duplicates(inplace=True)
phq9 = pd.read_csv("/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Emily Muther/Mental Health Screening/Data_Raw/PHQ-9_Full_Data_data_11-11-22.csv")
phq9 = phq9[['PAT_MRN_ID','CONTACT_DATE','AGE AT CONTACT ','PHQ-9 Total Score (calculated)','PHQ-9 Totals']]
phq9.dropna(axis=0,inplace=True)
phq9.drop_duplicates(inplace=True)
psc = pd.read_csv("/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Emily Muther/Mental Health Screening/Data_Raw/PSC_Full_Data_data_11-11-22.csv")
psc = psc[['PAT_MRN_ID','CONTACT_DATE','AGE AT CONTACT ','Score','PSC Totals']]
psc.dropna(axis=0,inplace=True)
psc.drop_duplicates(inplace=True)
# Merge
df = gad7.merge(phq9,on=['PAT_MRN_ID','CONTACT_DATE','AGE AT CONTACT '],how="outer")
df = df.merge(psc,on=['PAT_MRN_ID','CONTACT_DATE','AGE AT CONTACT '],how="outer")
# Rename
df.rename({'PAT_MRN_ID':'ID','CONTACT_DATE':'Date','AGE AT CONTACT ':'Age','GAD-7 Total Score':'GAD-7 Total','GAD-7 Totals':'GAD-7 Group','PHQ-9 Total Score (calculated)':'PHQ-9 Total','PHQ-9 Totals':'PHQ-9 Group','Score':'PSC-17 Total','PSC Totals':'PSC-17 Group'},inplace=True,axis=1)
# Write to CSV
df.to_csv("/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Emily Muther/Mental Health Screening/Data_Cleaned/cf_mental_health_screening.csv")
```
